### 2022-09-13 main/chapter_searches.tex
add bad p-value takes; use commands for atlas and lhcb

@@

>>>>

probability of compatibility~\cite{
HIGG-2018-04,
HIGG-2018-27,
IceCube2013search,
lhcb2021test,
cern2021test
}

mix $p$-value with posterior tail~\cite{lhcb2017test}

@@

lhcb2021test article: compatible with the SM prediction with a P value of 0.10\%
cern:  probability of around 0.1\% that the data is compatible with the Standard Model predictions
https://home.cern/news/news/physics/intriguing-new-result-lhcb-experiment-cern
